
## Data 605 - Assignment 9

**Hazal Gunduz**

**1. Exercise 11 (page 363) The price of one share of stock in the Pilsdorff Beer Company (see Exercise 8.2.12) is given by $Y_{n}$ on the nth day of the year. Finn observes that the differences $X_{n} = Y_{n+1} - Y_{n}$ appear to be independent random variables with a common distribution having mean µ = 0 and variance $σ^2 = 1/4$. If $Y_{1} = 100$, estimate the probability that $Y_{365}$ is **

**(a) ≥ 100.**

```{r}
# a.Greater than or equal to 100

1 - pnorm((100 - 100) / (0.5 * sqrt(365 - 1)))
```

P($Y_{365}$ ≥ 100) = 0.5

**(b) ≥ 110.**

```{r}
# b.Greater than or equal to 110

1 - pnorm((110 - 100) / (0.5 * sqrt(365 - 1)))
```

P($Y_{365}$ ≥ 110) = 0.147

**(c) ≥ 120.**

```{r}
# c.Greater than or equal to 120

1 - pnorm((120 - 100) / (0.5 * sqrt(365 - 1)))
```

P($Y_{365}$ ≥ 120) = 0.018

**2. Calculate the expected value and variance of the binomial distribution using the moment generating function.**

Moment generating function is:

$M_z(t) = Expected(e^{tx})$

Binomial distribution function is:

$P_{x} = {n \choose x} p^x (1 - p)^{n-x}$

Moment generating function and binomial distribution is:

$M_z(t) = \sum_{x=0}^{n} e^{tx} * {n\choose x} p^x (1 - p)^{n-x}$

M(t) = $(pe^{t} + 1 - p)^n$

M’(t) = $npe^{t}(pe^{t} - p + 1)^{n-1}$

M’(0) = $npe^0(pe^0 - p + 1)^{n-1} = np(p - p + 1)^{n-1} = np(1)^{n-1} = np$

$M^n(t) = npe^t(pe^t - p + 1)^{n-2}(npe^t - p + 1)$

$M^n(0) = npe^0(pe^0 - p + 1)^{n-2}(npe^0 - p + 1) = np(np - p + 1)$

Expected binomial distribution is $np$ and the variance is: $np(− p + 1)$

**3. Calculate the expected value and variance of the exponential distribution using the moment generating function.**

Exponential distribution is: 

$f(x) = λe^{-λx}$

Moment generating function is: 

$M(t) = \int_{0}^{\inf} e^{tx} * λe^{-λx} = - λ / t - λ$

Expected value is:

M′(t) =  $λ / (t -  λ)^2$

M′(0) = 1

$M^n(t) = - 2λ / (t - λ)^3$

$M^n(0) = - 2λ / (- λ)^3 = 2 / λ^2$

The expected value is $1 / λ$ and the variance is $2 / λ^2$

Rpubs =>  https://rpubs.com/gunduzhazal/1020243


